DATA 621 - Business Analytics and Data Mining

### 2020-11-26 Final_project/Draft_EDA_start.Rmd
Update to Header information

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #3'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg,
    Bryan Persaud, Jeff Shamp
date: "10/28/2020"
output:
  pdf_document: default
urlcolor: purple
---

@@

```{r load_data}
ca_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/CAvideos.csv"
ca_set <- read_csv(file = ca_path)
us_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/USvideos.csv"
us_set <- read_csv(file = us_path)
gb_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/GBvideos.csv"
gb_set <- read_csv(file = gb_path)
fr_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/FRvideos.csv"
fr_set <- read_csv(file = fr_path)
de_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/DEvideos.csv"
de_set <- read_csv(file = de_path)
```

@@

```{r summary_ca}
summaryca <- ca_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryca)

@@

```{r summary_de}
summaryde <- de_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryus)

@@

```{r ca_train_split}
#potential train/test split
ca_set_model <- ca_set %>%
  select(-title, -tags, -channel_title, -trending_date, -publish_time, -video_id, -thumbnail_link, -description, -country)

ca_smp_size <- floor(0.75*nrow(ca_set))
ca_ind <- sample(seq_len(nrow(ca_set)), size = ca_smp_size)

ca_train <- ca_set[ca_ind,]
ca_test <- ca_set[-ca_ind,]
```

>>>>

---
title: "DATA 621 - Business Analytics and Data Mining"
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg, 
  Bryan Persaud, Jeff Shamp
date: "12/14/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
subtitle: 'Fall 2020 - Group 2 - Final Project'
urlcolor: purple
---

@@

```{r load_data, message=FALSE}
ca_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/CAvideos.csv"
ca_set <- read_csv(file = ca_path)
us_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/USvideos.csv"
us_set <- read_csv(file = us_path)
gb_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/GBvideos.csv"
gb_set <- read_csv(file = gb_path)
fr_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/FRvideos.csv"
fr_set <- read_csv(file = fr_path)
de_path = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/DEvideos.csv"
de_set <- read_csv(file = de_path)
```

@@

```{r summary_ca, message=FALSE}
summaryca <- ca_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryca)

@@

```{r summary_de}
summaryde <- de_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summaryde)

@@

```{r ca_train_split}
#potential train/test split

ca_smp_size <- floor(0.75*nrow(summaryca))
ca_ind <- sample(seq_len(nrow(summaryca)), size = ca_smp_size)

ca_train <- summaryca[ca_ind,]
ca_test <- summaryca[-ca_ind,]
```
